\textbf{NBA Party}

### 2017-05-06 poster/poster.tex
Working version with data-information. Not yet working: model tables.

\documentclass[24pt, a0paper, portrait]{tikzposter} 
 \usepackage{algorithm2e} \usepackage{amsmath} \usepackage{amsthm} \usepackage{amsfonts} \usepackage{bbm} \usepackage{color,soul} \usepackage{framed} \usepackage{hyperref} \usepackage{mathtools} \usepackage[utf8]{inputenc} 
 \newtheorem{theorem}{Theorem}[section] \newtheorem{lemma}[theorem]{Lemma} \newtheorem{proposition}[theorem]{Proposition} \newtheorem{corollary}[theorem]{Corollary}  \DeclareMathOperator*{\argmin}{arg\,min} \DeclareMathOperator*{\argmax}{arg\,max} \newcommand{\D}{\mathrm{d}} \SetKwInput{KwInput}{Input} \SetKwInput{KwOutput}{Output}   \title{The effects of night-light on subsequent day sports performance} \author{Eric Lax, Andreas Santucci} \date{May 19th, 2017} \institute{Institute for Computational and Mathematical Engineering}   \usetheme{Board}   \begin{document}   \maketitle

\block{~} {     It's not unreasonable to think that game performance can be affected (in part) by what takes place off the court. We are interested to see if teams exhibit a decline in performance the day following a game in a party city. We exploit data on bookmaker spreads, the expected score differential between two teams after conditioning on observable performance. We expect a team to meet the spread half the time, since this is how bookmakers minimize risk on their end. We construct a model which attempts to estimate the causal effect of  visiting a "party-city" the day before a game on the probability of meeting the spread. }

\begin{columns}     \column{0.4}     \block{Data Sources}{
      Text and more text
      Text and more text
      Text and more text
      Text and more text
      Text and more text
      Text and more text
      Text and more text
      Text and more text
      Text and more text
    }       \column{0.6}     \block{NBA model}{Here, \vspace{4cm}} \end{columns}

\begin{columns}     \column{0.5}     \block{Profits on MLB Betting in 2016}     {         \begin{tikzfigure}             \includegraphics[width=0.4\textwidth]{figures/mlb_bets}         \end{tikzfigure}     }     \column{0.5}     \block{Description of the figure}{
      On the left, we plot profits as a function of time over the 2016 season. For each relevant
      game, we place a bet if our model instructs us of odds sufficiently different from what
      the betting house suggests. We account for the bookmaker's cut. In the early season,
      at its worst we are out of pocket \$750 dollars. By season end, we have recouped all of
      our initial investment plus an additional \$13.5k.
    }
    \note[         
      targetoffsetx=-8cm,          
      targetoffsety=-6.5cm,          
      width=0.5\linewidth         
    ]{e-mail: \texttt{santucci@stanford.edu}}   \end{columns}   \end{document}

>>>>

\documentclass[24pt, a0paper, portrait]{tikzposter} 
 \usepackage{algorithm2e} \usepackage{amsmath} \usepackage{amsthm} \usepackage{amsfonts} \usepackage{bbm} \usepackage{color,soul} \usepackage{framed} \usepackage{hyperref} \usepackage{mathtools} \usepackage[utf8]{inputenc} 
\usepackage{subcaption}
 \newtheorem{theorem}{Theorem}[section] \newtheorem{lemma}[theorem]{Lemma} \newtheorem{proposition}[theorem]{Proposition} \newtheorem{corollary}[theorem]{Corollary}  \DeclareMathOperator*{\argmin}{arg\,min} \DeclareMathOperator*{\argmax}{arg\,max} \newcommand{\D}{\mathrm{d}} \SetKwInput{KwInput}{Input} \SetKwInput{KwOutput}{Output}   \title{The effects of night-light on subsequent day sports performance} \author{Eric Lax, Andreas Santucci} \date{May 19th, 2017} \institute{Institute for Computational and Mathematical Engineering}   \usetheme{Board}   \begin{document}   \maketitle

\block{Idea} {     It's not unreasonable to think that game performance can be affected (in part) by what takes place off the court. We are interested to see if teams exhibit a decline in performance the day following a game in a party city. We exploit data on bookmaker spreads, the expected score differential between two teams after conditioning on observable performance. We expect a team to meet the spread half the time, since this is how bookmakers minimize risk on their end. We construct a model which attempts to estimate the causal effect of  visiting a "party-city" the day before a game on the probability of meeting the spread. }

\block{Mathematical Model}{
  \[
    \texttt{meet spread} \sim \texttt{party} + \substack{\texttt{days since} \\ \texttt{last game}} + \substack{\texttt{time}\\ \texttt{difference}} + \substack{\texttt{distance} \\ \texttt{traveled}}
  \]
}

\begin{columns}     \column{0.4}     \block{Data Sources}{
    \paragraph{Betting house data and game outcomes}
    We obtained data from 
    \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, 
    which records the outcome of each game alongside the line set by a betting house.

    \paragraph{Data which determines the night-life index of a city}
    We also obtained data from
    \href{https://www.bls.gov/data/}{Bureau of Labor Statistics} 
    which records the number of establishments by business type at the county-quarter level. As a 
    proxy for how much night-life there is in a city, we look toward the 
    number of sound recording studios, musical groups, and music publishers there 
    are for a particular county-year: we simply calculate the average number of establishments 
    across all three music categories listed above.

We then merge this in with our lines data, taking care to do so according to each season-team's last game location; we also lag our BLS data by one year.
To this data, we've created features such as 
the number of days since last game, the last game location, the travel distance, and
average age. Our data range from 2010-2011 season through present, which includes part of the 2016-2017 season.

\paragraph{Minutes data on player specific performance}
We also gathered minutes data from \href{http://www.espn.com/nba/scoreboard/_/date/}{ESPN}.
The minutes data also contain information on the number of free throws, field goals, and
three pointers made and attempted by each player in each game.

    }
    \column{0.6}     
    \block{NBA model}{
      Here,
      % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu % Date and time: Sat, May 06, 2017 - 09:58:05 AM

} 
\end{columns}

\begin{columns}   \column{0.4}
  \block{Player Specific Model}{
    Here
  }
  \column{0.6}
  \block{MLB Model}{
    Here
  } \end{columns}

\begin{columns}     \column{0.5}     \block{Profits on MLB Betting in 2016}     {         \begin{tikzfigure}             \includegraphics[width=0.4\textwidth]{figures/mlb_bets}         \end{tikzfigure}     }     \column{0.5}     \block{Description of the figure}{
      On the left, we plot profits as a function of time over the 2016 season. For each relevant
      game, we place a bet if our model instructs us of odds sufficiently different from what
      the betting house suggests. We account for the bookmaker's cut. In the early season,
      at its worst we are out of pocket \$750 dollars. By season end, we have recouped all of
      our initial investment plus an additional \$13.5k.
    }
    \note[         
      targetoffsetx=-8cm,          
      targetoffsety=-6.5cm,          
      width=0.5\linewidth         
    ]{e-mail: \texttt{santucci@stanford.edu}}   \end{columns}

\block{Meta Analysis}{
  Over 6k lines of code written, with ~120 commits.

  \begin{tikzfigure}
    \includegraphics[width=0.3\textwidth]{figures/gh_commits}
  \end{tikzfigure}
  \begin{tikzfigure}     \includegraphics[width=0.7\textwidth]{figures/punch_card}    \end{tikzfigure}
}

\end{document}
